---
title: "Theme showcase"
description: >
  A kitchen-sink of common documentation elements so you can see how the
  muted-blue theme styles headings, prose, code, tables, and figures — in both
  light and dark mode.
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.align = "center",
    fig.width = 7,
    fig.height = 4,
    dpi = 96
)
```

Use the **light switch** in the top-right of the navbar to flip between light,
dark, and auto modes. Every element on this page is styled for both.

## Prose and inline elements

This is a normal paragraph of body text set in **Inter**. It mixes *emphasis*,
**strong emphasis**, a [link to pkgdown](https://pkgdown.r-lib.org), and a bit
of `inline_code()` to show the muted-blue code chip. Headings are set in
**Outfit** with slightly tightened letter-spacing for a sleeker feel.

> Blockquotes get a muted-blue accent bar on the left, which reads cleanly
> against both the light off-white and the dark navy backgrounds.

### Lists

- An unordered list item
- Another item, with `inline code`
    - A nested item
    - One more nested item
- A final top-level item

1. First ordered step
2. Second ordered step
3. Third ordered step

## Code blocks

Fenced code blocks are framed with a rounded border that matches the rest of the
page. The token colours come from the `arrow-light` / `nord` syntax themes,
which track the active colour mode:

```{r}
# A short, plain example
nums <- rnorm(100, mean = 5, sd = 2)
summary(nums)
```

A non-evaluated block, to show pure syntax highlighting:

```r
fit <- lm(mpg ~ wt + cyl, data = mtcars)
coef(summary(fit))
```

## Tables

```{r}
knitr::kable(head(mtcars[, 1:5]), caption = "The first few rows of `mtcars`.")
```

A plain Markdown table renders the same way:

| Mode  | Background  | Primary   |
|-------|-------------|-----------|
| Light | `#fbfcfe`   | `#3f6f9f` |
| Dark  | `#0f141b`   | `#7ea8d6` |

## Figures

```{r}
op <- par(mar = c(4, 4, 1, 1))
plot(mtcars$wt, mtcars$mpg,
    pch = 19, col = "#3f6f9f",
    xlab = "Weight (1000 lbs)", ylab = "Miles per gallon"
)
par(op)
```

## Buttons and emphasis

<a href="#" class="btn btn-primary">Primary button</a>
<a href="#" class="btn btn-outline-primary">Outline button</a>

That covers the elements you'll meet most often in package documentation.
